\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-24 demystify.tex
updates
Updates from Overleaf

If you don't know the professor (e.g., first email contact), then use \textbf{Prof. Lastname} or \textbf{Dr. Lastname}. I've seen many international students write \textbf{Prof.} or \textbf{Dr.} \textbf{Firstname Lastname}.  Writing like that makes it like you copy and paste names, so no need to do so,  just Prof. or Dr. Lastname.
Moreover, if you don't know the prof., do not use Mr. or Mrs., or Firstname---to me it seems a bit disrespectful. As you get to know that prof. better and depends on their preference, you may call them by their firstname.  For example, my students and colleague call me Vu. Some students call me \emph{Dr. Vu}, which I find a bit amusing but am totally fine with it.

Note that at some universities, especially those that do not offer PhD degrees, will use the formal \textbf{Dr.} title, i.e., Dr. Lastname.  So just observe and follow how it is done at your place.  Also note that some faculty might not have a Ph.D. and so you can use Prof. Lastname instead.

>>>>

If you're reaching out to a professor for the first time,  address them as either Prof. Lastname or Dr. Lastname. I've noticed that many international students tend to use the titles Prof. or Dr. FirstName LastName, but this can come across as if you're simply copying and pasting names. It's not necessary, so stick with Prof. or Dr. Lastname.

Furthermore, it's important to avoid using Mr. or Mrs., or the professor's first name if you're not acquainted with them yet. This approach may be seen as somewhat disrespectful, especially in academic fields where most professors hold advanced degrees. As you become more familiar with a professor and depending on their preferences, you may transition to addressing them by their first name. For instance, my students and colleagues call me Vu. Some students also refer to me as Dr. Vu, which I find somewhat amusing but am perfectly fine with.

Note that in some universities, e.g., those that do not offer PhD degrees, the formal title Dr. Lastname is commonly used. It's essential to observe and follow the conventions at your particular institution. Additionally, be aware that not all faculty members may hold a Ph.D., in which case using Prof. Lastname is a suitable alternative.
